---
title: "R Notebook"
output: html_notebook
---

## Application Program Interface

two software communicate with each other

For example, the way pandas library works.

```{python}

import pandas as pd

dict1 = {"abc": [1, 2, 3], "def": [4, 5, 6]}

df = pd.DataFrame(dict1)

df.head()
```

REST APIs

Respresentational State Transfer APIs

HTTP is the way of communication. You send a message to web service API, it performs the process and return the message with HTTP, and data in JSOn format.


## An example COIN Gecko API

```{python}
# import coingecko library

!pip install pycoingecko
from pycoingecko import CoinGeckoAPI

# create a client object
cg = CoinGeckoAPI()   

bitcoin_data = cg.get_coin_market_chart_by_id(id = "bitcoin",
vs_currency = "usd", days = 30)

# data will be downloaded in JSON format

# We are interested in price
bitcoin_data['price']

data = pd.DataFrame(bitcoin_price_data, columns = ['TimeStamp', 'Price'])

data['Date'] = pd.to_datetime(data['TimeStamp'], units = 'ms')


## candle stick

candlestick_data = data.groupby(data.Date.dt.date).agg({'Price': ['min', 'max', 'first', 'last']})


## Use plotly to make a chart

fig = go.Figure(data = [go.Candlestick(x = candlestick_data.index,
open = candlestick_data['Price']['first'],
high = candlestick_data['Price']['max'],
low = candlestick_data['Price']['min'],
close = candlestick_data['Price']['last']) ])

fig.update_layout(xaxis_rangeslider_visible = False, xaxis_title = 'Date',
yaxis_title = 'Price (USD $)', title = 'Bitcoin Candlestick Chart Over Past 30 Days')

plot(fig, filename = 'bitcoin_candlestick_graph.html')

```


# API keys and requests

API key is way to access the API. API uses the key to identify the requester.

## Watson Text to Speech API

```{r}
from ibm_watson import SpeechToTextV1

url_s2t = "https://stream.watsonplatform.net/speech-to-text/api"

key_s2t = "Eocixxxxxxxxxxxx"

s2t = SpeechToTextV1(iam_apikey = key_s2t, url = url_s2t)

filename = "hello_this_is_python.wav"

with open(filename, mode = "rb") as wav:
    response  = s2t.recognize(audio = wav, content_type = 'audio/wav')
```

```{r}
recognized_text = responde.result['ressults'][0]['alternatives'][0]['transcript']
```

## language translator

```{r}
from ibm_watson import LanguageTranslatorV3

url_lt = "hrrps://gateway.watsonplatform.net/language-translator/api"

api_key = 'sdfbkfbkjwbefkqjkqejfkqjrbgkr'

version_lt = '2018-05-01'

language_translator = LanguageTranslatorV3(iam_apikey = api_key, url = url_lt, version = version_lt)

language_translator.list_identifiable_language().get_result()


recognized_text = "hello this is python"

translation_response = language_translator.translate(text = recognized_text, model_id = 'en-es')



translation = translation_response.get_result()
translation

spanish_translation = translation['translations'][0]['translation']

translation_new = language_translator.translate(text = spanish_translation, model_id = 'es-en').get_result()

translation_eng = translation_new['translations'][0]['translation']
translation_eng


french_translation = language_translator.translate(text = translation_eng, model_id = 'en-fr').get_result()
french_translation['translations'][0]['translation']


```




### HTML for web scraping

We need to understand the how webpages are built with html. There are tags where data is stored in each section. we need to know that which tags are important to us.

<h?>  headlines
<p> paragraph
<body>
<a href = "https://www.ibm.com"> ibm webpage </a>
 
### HTML tables

<table>
    <tr>
        <td> cells
        <td> cells


## what is web scraping

`from bs4 import BeautifulSoup`
`html = "url string"`

parse

soup = BeautifulSoup(html, 'html5lib')

title = soup.title
soup.h3

sibling = tag_object.next_sibling


tag_child.attrs


tag_child.string

**`find_all`**
```
table_row = table.find_all(name = "tr")
table_row

first_row = table_row[0]
first_row
```

Iterate through table rows

```
for i, row in enumerate(table_rows):

    print("row", i)
    cells = row.find_all("td")
    
    for j, cell in enumerate(cells):
    
        print("column", j, "cell", cell)
    
    
    
    
    
    
    
    

```








